Musical Genres as Fuzzy Categories

### 2025-05-05 heidelberg-slides.qmd
a buncha

@@

## Correspondence Plot of Genre Column Scores
![First and Fourth Dimensions](Plots/ca-genre-col14.png)

## Correspondence Plot of Label Column Scores
![First and Fourth Dimensions](Plots/ca-label-col14.png)

## Correspondence Plot of Genre Column Scores
![First and Second Dimensions](Plots/genre-sim-dens12.png)

## Correspondence Plot of Label Column Scores
![First and Second Dimensions](Plots/label-sim-dens12.png)

## Correspondence Plot of Genre Clouds
![First and Second Dimensions](Plots/genre-proto12.png)

## Correspondence Plot of Genre Clouds
![First and Third Dimensions](Plots/genre-proto13.png)

## Correspondence Plot of Genre Clouds
![First and Fourth Dimensions](Plots/genre-proto14.png)

## Correspondence Plot of Label Clouds
![First and Second Dimensions](Plots/label-proto12-1.png)

## Correspondence Plot of Label Clouds
![First and Second Dimensions](Plots/label-proto12-2.png)

## Correspondence Plot of Label Clouds
![First and Third Dimensions](Plots/label-proto13.png)

## Correspondence Plot of Label Clouds
![First and Fourth Dimensions](Plots/label-proto14.png)

## Genre Ridge Plot
![First Dimension](Plots/genre-ridge-dim1.png)

## Genre Ridge Plot
![Second Dimension](Plots/genre-ridge-dim2.png)

## Genre Ridge Plot
![Third Dimension](Plots/genre-ridge-dim3.png)

## Label Ridge Plot
![First Dimension](Plots/label-ridge-dim1.png)

## Label Ridge Plot
![Second Dimension](Plots/label-ridge-dim2.png)

## Label Ridge Plot
![Third Dimension](Plots/label-ridge-dim3.png)

>>>>

## Mondo Breiger Approach

- Each individual provides a "personal" two mode network of genres by social labels with corresponding affiliation matrix $\mathbf{A}(p)$
  - $a^{(p)}_{gl} = 1$ if individual $p$ associates genre $g$ with label $l$
- The personal genre projection is given by:
  - $\mathbf{G}(p) = \mathbf{A}(p)\mathbf{A}(p)^T$
  - $g^{(p)}_{ij}$ records the $p^{th}$ individual's perceived similarity between genres $i$ and $j$ based on their shared labels
  - $g^{(p)}_{ii}$ records the number of times individual $p$ associates genre $i$ with a label

## Mondo Breiger Approach

- Each individual provides a "personal" two mode network of genres by social labels with corresponding affiliation matrix $\mathbf{A}(p)$
  - $a^{(p)}_{gl} = 1$ if individual $p$ associates genre $g$ with label $l$
- The personal label projection is given by:
  - $\mathbf{L}(p) = \mathbf{A}(p)^T\mathbf{A}(p)$
  - $l^{(p)}_{kl}$ records the $p^{th}$ individual's perceived similarity between labels $k$ and $l$ based on their shared genres
  - $l^{(p)}_{kk}$ records the number of times individual $p$ associates genre $i$ with a label

## Individual Matrix Examples (Two Mode)
:::: {.columns}
::: {.column width="50%"}
![id_65](Plots/data-ex1.png)
:::
::: {.column width="50%"}
![id_236](Plots/data-ex2.png)
:::
::::

## Individual Matrix Examples (Two Mode)
:::: {.columns}
::: {.column width="50%"}
![id_1114](Plots/data-ex3.png)
:::
::: {.column width="50%"}
![id_2002](Plots/data-ex4.png)
:::
::::

## Example Row Projection
:::: {.columns}
::: {.column width="50%"}
![id_65](Plots/data-ex1.png)
:::
::: {.column width="50%"}
![id_65](Plots/data-ex1-rp.png)
:::
::::

##  Example Column Projection
:::: {.columns}
::: {.column width="50%"}
![id_65](Plots/data-ex1.png)
:::
::: {.column width="50%"}
![id_65](Plots/data-ex1-cp.png)
:::
::::

##  Example Row Projection
:::: {.columns}
::: {.column width="50%"}
![id_236](Plots/data-ex2.png)
:::
::: {.column width="50%"}
![id_236](Plots/data-ex2-rp.png)
:::
::::

##  Example Column Projection
:::: {.columns}
::: {.column width="50%"}
![id_65](Plots/data-ex2.png)
:::
::: {.column width="50%"}
![id_65](Plots/data-ex2-cp.png)
:::
::::

##  Stacked Matrices Examples
:::: {.columns}
::: {.column width="50%"}
![id_65 and id_236 (Rows)](Plots/data-ex-stack1.png)
:::
::: {.column width="50%"}
![id_65 and id_236 (Columns)](Plots/data-ex-stack2.png)
:::
::::

@@

## Correspondence Plot of Genre Clouds
![First and Second Dimensions](Plots/genre-proto-ex1.png)

## Correspondence Plot of Genre Clouds
![First and Second Dimensions](Plots/genre-proto-ex2.png)

## Correspondence Plot of Genre Clouds
![First and Second Dimensions](Plots/genre-proto-ex3.png)

## Correspondence Plot of Label Clouds
![First and Second Dimensions](Plots/label-proto-ex1.png)

## Correspondence Plot of Label Clouds
![First and Second Dimensions](Plots/label-proto-ex2.png)

## Correspondence Plot of Label Clouds
![First and Second Dimensions](Plots/label-proto-ex3.png)

## Correspondence Plot of Label Clouds
![First and Second Dimensions](Plots/label-proto-ex4.png)
